\renewcommand{\abstractname}{\bf \Large Abstract}
\begin{abstract}

\emph{U Network}\footnote{\emph{U Network}: http://www.u.network} is the revolutionary content-value based prediction market platform and a content-incentive ecosystem driven by value. \emph{U Community} is the first digital asset platform powered by \emph{U Network}.

\emph{U Network} leverages the blockchain technology to build a prediction market of user-generated content. By constructing a more effective pricing system for the generated content, users are motivated to discover and promote high-value contents by sharing it with other participants in the network. In particular, \emph{U Community} is built on top of \emph{U Network}, which consist of four types of participants: content creators, content explorer, community moderators and regular user. All these participants interact with each other and build the community. With the help of prediction market, content creators and explorers are encouraged to keep generating and discovering high-quality contents in \emph{U Community}, therefore, offering plenty of value to regular users. Community moderators are periodically selected from regular users and entitled with important privilege(e.g., deleting improper contents) to maintain the normal operation of community. Moreover, a voting-based appeal mechanism is built to prevent abusing their privilege. As monetized incentive, regular users need to pay tokens of \emph{U Network} to access valuable contents, while content creators, explorers and moderators will be rewarded with tokens for their services.

The goal of \emph{U Network} is to build a decentralized user-generated-content blockchain platform where users are encouraged to create and explore valuable contents with monetized incentive. \emph{U Community} will be the first application built on this platform with high-accessibility, high-scalability, and low latency.


\vspace{1cm}

\textbf{Keywords:} Digital Asset, Prediction Market, Blockchain, Monetized Incentive
\end{abstract}