\chapter{To-Do List}

The \emph{U  Network} is an open-source project that can be found at ``https://github.com/U-Network/UNetwork''. At the early stage of development, there are many tasks need to be finished. Partial work on the list is following:


\begin{enumerate}

\item {\bf Revision of Document}: 
\begin{enumerate}
\item Revise README document and composite a short version. It should clearly explain the fundamental blockchain system of  \emph{U  Network}, provide summary of features, and point out future directions. 
\item Remove docus/specification directory.
\item Add more documents regarding testing and deployment of  \emph{U  Network}.
\end{enumerate}

        

\item {\bf Coding Style Convention}: 
\begin{enumerate}
\item Current coding style is inconsistent. It is advisable to modify the entire code repository.
\item Suggested Golang coding standard: 

\textit{https://github.com/golang/go/wiki/CodeReviewComments}
\end{enumerate}

\item {\bf Redundant Code Removal}:
\begin{enumerate}
\item remove directories: cli/LevelDBQuery, cli/consensus, consensus/sbft, net/rpt\_test
\item remove files: account/account\_test.go, consensus/policy.go, consensus/policyLevel.go, core/transaction/txAttribute\_test.go
\end{enumerate}

\item {\bf Continuous Integration}:
\begin{enumerate}
\item Use Travis CI to automatically compile and build after each check-in delivery.
\end{enumerate}


\item {\bf Bug Fix and Improvement}:
\begin{enumerate}
\item  move the hash generation of transaction into core/transaction/TransactionBuilder.go
\item  enforce consistent address format of registered asset, such as prefix.
\item modify the redundant interface of RPC. 
\end{enumerate}


% external end
\end{enumerate}


\clearpage
