\chapter{Future Direction and Roadmap}

\section{Future U Network Evolution}
As the exponential growth of information continues in the next few years, we believe \emph{U Network} is the best solution to the problems of traditional user-generated-contents communities. With the blockchain technology and economic incentive model, \emph{U Network} constructs a content-valuation prediction market. It provides reasonable incentives to valuable-content creators, and motivates the regular user audience to explore and promote high-quality contents. Therefore, high-quality contents can easily stand out and all contributors receive their monetized rewards in the \emph{U Network}.

Moreover,  \emph{U Network} construct an ``user-generated-content public blockchain'', which serves as the framework and platform of future content-oriented communities and applications. In particular,  \emph{U Community} will be the first application using  \emph{U Network} platform which focuses on the content information of digital assets.

In the long term,  \emph{U Network}  will fully utilize the distributed storage protocol to further improve the decentralized platform infrastructure, which emphasize on data integrity and user privacy.  In addition, innovative consensus algorithm will be implemented to further expedite the transaction speed and enhance the reliability of transactions. Moreover, performance optimization will be proposed for decentralized search algorithm, therefore, making it more efficient to identify up-voters for valuable contents. 

\section{Future Application Use Case}
In the era of information explosion, \emph{U Network} opens the door to a huge market for user-generated contents. It is an revolutionary trend to empower creators, distributors and explorer of high-quality contents, who are the driving force of future valuable-content communities. Therefore, all existing communities and applications can be revolutionized using \emph{U Network} in different industries. 

 \subsection{Communities for Valuable Digital Literature}
For communities with constantly updated series of literature contents, it's imperative to rate the published content and motivate the author to maintain the quality in the following release. By introducing \emph{U Network} rating and rewarding system, top-selling authors can receive a long-term incentive and reasonable returns.  


 \subsection{ Communities for Digital Asset}
More people include digital assets, such as crypto-currency\cite{bitcoin,eth,eth2}, into their asset portfolio in the past decade. Those people need a community to gather reliable information, exchange opinions and learn from professionals. However, existing communities are notorious for fake information and fraudulence. Users find it very challenging to identify reliable and valuable information. As such, \emph{U Network} provides the best solution as high-quality contents can be discovered easily and promoted to more audience.  

 \subsection{Communities for Knowledge Sharing}
There are some issues with existing knowledge-sharing communities like Quora and Zhihu: authors have no direct and reliable approach to convert their knowledge into monetized rewards. In this scenario, \emph{U Network} can reward creators of valuable contents based on its rating and reward incentive mechanism. 

 \subsection{Communities for Social Media}
Existing social media communities such as blog and forum are important for regular Internet users to broadcast their own contents. With \emph{U Network} framework, these communities can construct their own rating and reward mechanism. As such, contributors of valuable contents in these existing communities can receive profit rewards. 

 \subsection{Communities for Intelligent Property}
Current society respect the original ownership of intelligent property, such as music, video, and articles. Nearly all these contents need content rating mechanism to discover and recommend high-quality ones. These communities can easily integrate \emph{U Network} framework and setup their own rating and reward system for specific intelligent property. 


\section{Roadmap}

	\begin{itemize}

	\item Jun 2015 to now, \emph{U  Network} team has been focusing on technology contents which had attracted more than 4 million active users. 
	\item Aug 2017, partnered with Huobi, we presented ``From 0 to 1, learn blockchain technology in a comprehensive way''. Over 10,000 paid students have completed the program. 
	\item Sept 2017, we launched ``Smart Contract Development'' education program. More than 180 blockchain developers had graduated from this program.    
	\item Jan 2018, we had hold ``Blockchain Connect'' China-US blockchain summit in San Francisco.
	\item Aug 2018, \emph{U  Network} Testnet release
	\item Nov 2018, \emph{U  Network} Mainnet release
	\item Dec 2018, \emph{U Community}  Alpha version release. 
	\item Feb 2019, \emph{U  Network} optimized Mainnet release
	\item May 2019, \emph{U Community} Beta version release, supports co-investing functionality
	\item Aug 2019, Completing \emph{U  Network} Mainnet and developer tool kits,
	\item Dec 2019, Build \emph{U  Network} ecosystem, import \emph{U  Network} into exisiting UGC platforms. 
\end{itemize}